Bayesian model in JAGS

### 2023-01-27 4_RSV_disease_burden/4_RSV_disease_burden.Rmd
update

For example, if we would like to estimate the baseline hospitalizations $\beta_{0jk}$ in age $j$ and socioeconomic group $k$, we can treat this parameter as (1) independent, meaning that the baseline hospitalizations are different in each group and we will need to estimate 27 parameters $\beta_{0j=1,k=1}$, $\beta_{0j=1,k=2}$...$\beta_{0j=9,k=3}$, (2) the same, meaning that the baseline hospitalizations are the same in all age and socioeconomic group and we will only need to estimate one parameter $\beta_0$, and (3) random draws from the a normal distribution, meaning that baseline hospitalizations are normally distributed in the whole population and baseline hospitalization of each subpopulation $jk$ is an realization of the distribution (a point in the distribution). In this case, we will estimate the mean and variations of the normal distribution and then get the subpopulation estimates.

>>>>

For example, if we would like to estimate the baseline hospitalizations $\beta_{0jk}$ in age $j$ and socioeconomic group $k$, we can treat this parameter as (1) independent, meaning that the baseline hospitalizations are different in each group and we will need to estimate 27 parameters $\beta_{0j=1,k=1}$, $\beta_{0j=1,k=2}$...$\beta_{0j=9,k=3}$, (2) the same, meaning that the baseline hospitalizations are the same in all age and socioeconomic group and we will  estimate one parameter $\beta_0$, and (3) random draws from the a normal distribution, meaning that baseline hospitalizations are normally distributed in the whole population and baseline hospitalization of each subpopulation $jk$ is an realization of the distribution (a point in the distribution). In this case, we will estimate the mean and variations of the normal distribution and then get the subpopulation estimates.
\
\
If we model the parameters in Bayesian framework, the third scenario corresponds to a Hierarchical Bayesian model.

## Background knowledge of Hierarchical Bayesian regression: Benefits

From the aforementioned example, e
